A Survey of Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
Fixed ALL of analysis, taking out 17-year old boy.

\title{A Survey Wearable Device Risk Perceptions}
%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}

@@

\section{Results}
%%%confusing runthrough of the results.. is this too packed. I wrote a roadmap paragraph instead based on this, which is below. Much better.

%Overall, we observed that any photos, videos, audio recordings, or financial information is considered to be highly sensitive, whereas publicly deducible traits, such as the language being spoken, gender, and age, were considered the least sensitive.  Additionally, participants considered data shared to be equally upsetting, regardless if the recipients were friends, work contacts, or the public. Although in some cases, asking about wearables or smart phones did elicit unique reactions to the situation from participants, the device generally does not contribute to the severity of the threat. When assessing new technologies as a whole, participants assessed many of the new technologies similarly as low risk and low benefit. Through our open-ended question, we find that the number one self-reported concern when owning and interacting with wearable devices is the loss of privacy.

In this section, we present our survey results. We first discuss participants' responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived. Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies. We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.

@@

\subsubsection{Data Recipient}
Based on our data, we observed that the largest effect seemed to stem from who the recipient of the data was: across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.4\%), work contacts (75.1\%), and the public (72.4\%) were much higher. A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}). However, these effect sizes were relatively small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).

%Comment on independence of observations, differences between public/work, and end the subsection

@@

%SE: this needs to be rewritten below.

@@

% LL: I thought this would be better, but then it looked stupid, so I commented it out.

%\begin{table}[t]
%\begin{center}
%\begin{tabular}{|l|c|}
%\hline
%Recipients	& VUR \\
%\hline
%App	& 42.3\% \\
%Friends & 69.4\% \\
%Work & 75.1\% \\
%Public & 72.4\% \\
%\hline
%\end{tabular}
%\caption{VUR rates by recipient.}
%\label{whomVUR}
%\end{center}
%\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
\hline
Work-App	& 564.32 & <0.0001 & 5,085 & 0.111\\
Public-App	& 479.98 & <0.0001 & 5,192 & 0.092\\
Friends-App & 380.00 & <0.0001 & 5,098 & 0.075\\
Friends-Work & 20.37 & <0.0001 & 5,039 & 0.004\\
Friends-Public & 5.35 & <0.0207 & 5,146 & 0.001\\
Work-Public&  5.05 & <0.0246 & 5,133	& 0.001\\
\hline
\end{tabular}
\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
\label{recipient}
\end{center}
\end{table}

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{| l | c |}

<data> &  VUR  \\
a video of you unclothed & 95.97\% \\
bank account information & 95.91\% \\
social security number & 94.84\% \\
video of you entering in your PIN & 92.67\% \\
a photo of you unclothed & 92.59\% \\
an incriminating/embarrassing photo of you & 91.39\% \\
username and password for websites & 89.55\% \\
credit card information & 88.98\% \\
an incriminating/embarrassing video of you & 88.41\% \\
a random (inward-facing) photo you at home & 87.50\% \\

\end{tabular}
\caption{A table of the top 10 upsetting <data> types, irregardless of recipient or data type.}
\label{top10}
\end{center}
\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{| l | c |}
%starting from #63
<data> &  VUR  \\
eye movement patterns (for eye tracking) & 40.51\% \\
when and how much you exercise  & 38.66\% \\
when you are happy or having fun  & 34.51\% \\
which television shows you watch & 30.20\% \\
when you are busy or interruptible  & 29.50\% \\
music from your device  & 28.06\% \\
your heart rate & 27.50\% \\
your age & 24.29\% \\
the language you speak & 15.86\% \\
your gender & 14.91\% \\

\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, irregardless of recipient or data type.}
\label{bottom10}
\end{center}
\end{table}

@@

\subsubsection{Device Type}
Participants had unique VUR rates for situations only differing in the device. Our participants had a 70.23\% VUR when asked about wearables devices and 40.62\% VUR when asked about smartphones.The VUR rates for both devices for all 5 quesions are in table ~\ref{deviceVUR}. However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}). Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.  The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions. There were too few instances where a participant got both versions of questions (34 in total for all 5 questions), to be able to perform a within-subjects analysis.

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c |}
 Question &  Wearable VUR & Smartphone VUR \\
 All & 70.23\% & 40.62\%\\
Q1 & 14.81\%  &  6.13\%\\
Q2 & 44.11\%  &  19.85\%\\
Q3 & 87.09\%  &  58.44\%\\
Q4 & 52.77\%  & 55.79\%\\
Q5 & 86.49\%  &  91.82\%\\ 
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{deviceVUR}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c | c |}
%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
%All	2.814	0.1395	No		3589		0.001\\
%Q1	2.500	0.1139	No		714		0.004\\
%Q2	17.333	<0.0001	Yes		708		0.024\\
%Q3	0.020	0.8886	No		699		0.000\\
%Q4	1.426	0.2324	No		731		0.002\\
%Q5	1.611		0.2043	No		710		0.002\\
Question & $\chi^2$ &	2-tail P & Effect Size\\
All & 2.814 & 0.1395 & 0.001\\
Q1 & 2.500 & 0.1139 & 0.004\\
Q2 & 17.333 & <0.0001 & 0.024\\
Q3 & 0.020 & 0.8886 & 0.000\\
Q4 & 1.426 & 0.2324 & 0.002\\
Q5 & 1.611 & 0.2043 & 0.002\\
\end{tabular}
\caption{Results of the effects of <device> type contributing to VUR. Values are Chi-Square test results for between-subjects comparisons for participants who received one question, but not the other.}
\label{betweendevice}
\end{center}
\end{table}

@@

%% I EDITED THESE NUMBERS for 17 year old

\begin{table}[h]
\begin{center}
\begin{tabular}{lll}

Concern &  Responses &  Frequency   \\
Privacy & 452 & 25.32\% \\
Being Unaware & 275 & 15.40\ \\
%Unaware Use & 167 & (9.36\%)\\
%Unaware Collection & 64 & (3.59\%)\\
%Unaware Access & 44 & (2.46\%)\\
Health Risk & 191 & 10.70\%\\
Safety & 185 & 10.42\%\\
Financial Cost & 151 & 8.46\%\\
Security &	144 & 8.07\%\\
Social Impact &	157 & 8.80\%\\
Accidental Sharing &	69 & 3.87\%\\
Miscellaneous &	57 & 3.19\%\\
None	& 51 & 2.86\%\\
Social Stigma &	39 & 2.18\%\\
False Information & 33 & 1.85\%\\
Don't know & 31 & 1.74\%\\
Aesthetics 	& 19 & 1.06\%\\
Don't care 	& 11 & 0.62\%\\

\end{tabular}
\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
\label{open-responses}
\end{center}
\end{table}

>>>>

\title{A Survey of Wearable Device Risk Perceptions}
%\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}

@@

\section{Results}
In this section, we present our survey results. We first discuss participants' responses to the various data-sharing scenarios, and how data type, device type, and recipient contributed to how threatening a situation was perceived. Next, we discuss participants' risk/benefit assessment of various new technologies relative to well-established technologies. We conclude the section with participants' self-reported concerns about the biggest risks in owning wearable devices.

@@

\subsubsection{Data Recipient}
Based on our data, we observed that the largest effect seemed to stem from who the recipient of the data was: across all scenarios, 42.3\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (69.5\%), work contacts (75.2\%), and the public (72.4\%) were much higher. A chi-square test indicated that these differences were statistically significant (Table \ref{recipient}). However, these effect sizes were relatively small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).

@@

%Comment on differences between public/work, and end the subsection
%SE: this needs to be rewritten below.

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
\hline
Recipients	& $\chi^2$ & p-value 	& n & $\phi$ \\
\hline
Work-App	& 565.910 & <0.0001 & 5,083 & 0.111\\
Public-App	& 481.776 & <0.0001 & 5,1988& 0.093\\
Friends-App & 381.653 & <0.0001 & 5,096 & 0.075\\
Friends-Work & 20.39 & <0.0001 & 5,037 & 0.004\\
Friends-Public & 5.41 & <0.0200 & 5,142 & 0.001\\
Work-Public&  5.00 & <0.0253 & 5,129	& 0.001\\
\hline
\end{tabular}
\caption{Results of a chi-square test to examine VUR based on data recipient, across all data points.}
\label{recipient}
\end{center}
\end{table}

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{| l | c |}
\hline
<data> &  VUR  \\
\hline
a video of you unclothed & 95.97\% \\
bank account information & 95.91\% \\
social security number & 94.84\% \\
video of you entering in your PIN & 92.59\% \\
a photo of you unclothed & 92.59\% \\
an incriminating/embarrassing photo of you & 91.39\% \\
username and password for websites & 89.55\% \\
credit card information & 88.98\% \\
an incriminating/embarrassing video of you & 88.41\% \\
a random (inward-facing) photo you at home & 87.50\% \\
\hline
\end{tabular}
\caption{A table of the top 10 upsetting <data> types, irregardless of recipient or data type.}
\label{top10}
\end{center}
\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{| l | c |}
%starting from #63
\hline
<data> &  VUR  \\
\hline
eye movement patterns (for eye tracking) & 40.51\% \\
when and how much you exercise  & 38.66\% \\
when you are happy or having fun  & 34.75\% \\
which television shows you watch & 30.20\% \\
when you are busy or interruptible  & 29.50\% \\
music from your device  & 28.06\% \\
your heart rate & 27.50\% \\
your age & 24.29\% \\
the language you speak & 15.86\% \\
your gender & 15.00\% \\ 
\hline
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, irregardless of recipient or data type.}
\label{bottom10}
\end{center}
\end{table}

@@

\subsubsection{Device Type}
Participants had unique VUR rates for situations only differing in the device. Our participants had a 58.79\% VUR when asked about wearables devices and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}. However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}). Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.  The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions. There were too few instances where a participant got both versions of questions (34 in total for all 5 questions), to be able to perform a within-subjects analysis.

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | r | r |}
\hline
 Question &  Wearable VUR & Smartphone VUR \\
 \hline
 All & 58.79\% & 46.64\%\\
Q1 & 14.81\%  &  6.13\%\\
Q2 & 44.11\%  &  19.85\%\\
Q3 & 87.09\%  &  58.44\%\\
Q4 & 52.77\%  & 55.74\%\\
Q5 & 86.49\%  &  91.82\%\\ 
\hline
\end{tabular}
\caption{A table of the bottom 10 upsetting <data> types, respect to <recipient> app's server only (didn't share it with anyone else).}
\label{deviceVUR}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
%All	2.814	0.1395	No		3589		0.001\\
%Q1	2.500	0.1139	No		714		0.004\\
%Q2	17.333	<0.0001	Yes		708		0.024\\
%Q3	0.020	0.8886	No		699		0.000\\
%Q4	1.426	0.2324	No		731		0.002\\
%Q5	1.611		0.2043	No		710		0.002\\
\hline
Question & $\chi^2$ & 2-tail P & n  & Effect Size\\
\hline
All & 2.202 & 0.1378 & 3588 & 0.001\\
Q1 & 2.500 & 0.1139 & 714 & 0.004\\
Q2 & 17.333 & <0.0001 & 708 &  0.024\\
Q3 & 0.020 & 0.8886 & 699 &  0.000\\
Q4 & 1.413 & 0.2345 & 730& 0.002\\
Q5 & 1.604 & 0.2054 & 709 & 0.002\\
\hline
\end{tabular}
\caption{Results of the effects of <device> type contributing to VUR. Values are Chi-Square test results for between-subjects comparisons for participants who received one question, but not the other.}
\label{betweendevice}
\end{center}
\end{table}

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|r|r|}
\hline
Concern &  Responses &  Frequency   \\
\hline
Privacy & 452 & 25.32\% \\
Being Unaware & 275 & 15.40\ \\
%Unaware Use & 167 & (9.36\%)\\
%Unaware Collection & 64 & (3.59\%)\\
%Unaware Access & 44 & (2.46\%)\\
Health Risk & 191 & 10.70\%\\
Safety & 185 & 10.42\%\\
Financial Cost & 151 & 8.46\%\\
Security &	144 & 8.07\%\\
Social Impact &	157 & 8.80\%\\
Accidental Sharing &	69 & 3.87\%\\
Miscellaneous &	57 & 3.19\%\\
None	& 51 & 2.86\%\\
Social Stigma &	39 & 2.18\%\\
False Information & 33 & 1.85\%\\
Don't know & 31 & 1.74\%\\
Aesthetics 	& 19 & 1.06\%\\
Don't care 	& 11 & 0.62\%\\
\hline
\end{tabular}
\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
\label{open-responses}
\end{center}
\end{table}
